Think deep for reef resilience

### 2025-06-27 paper/paper_draft.qmd
Edit scripts to allow generation of figures from shared results data
Additionally remove management and gbr scale analyses from the quarto paper document.

Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).

In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially lower mean thermal tolerance levels compared to reefs in other clusters. However, many bioregions do not show strong differences in thermal tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; @sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol; @sfig-noresm2-mm-bioregion-dhwtol).

@@

Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi; @sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi; @sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity; @sfig-access-cm2-bioregion-totalconnectivity; @sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity; @sfig-noresm2-mm-bioregion-totalconnectivity).

## Management area scale clustering

@@

The clusters identified with timeseries clustering at the GBR scale show similar patterns to clusters identified at bioregion and management area scales. Reef depth (@sfig-access-esm1-5-gbr-depth; @sfig-access-cm2-gbr-depth; @sfig-ec-earth3-veg-gbr-depth; @sfig-gfdl-cm4-gbr-depth; @sfig-noresm2-mm-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor; @sfig-access-cm2-gbr-dhwcor; @sfig-ec-earth3-veg-gbr-dhwcor; @sfig-gfdl-cm4-gbr-dhwcor; @sfig-noresm2-mm-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion; @sfig-access-cm2-gbr-initialproportion; @sfig-ec-earth3-veg-gbr-initialproportion; @sfig-gfdl-cm4-gbr-initialproportion; @sfig-noresm2-mm-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels. There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean; @sfig-access-cm2-gbr-dhwmean; @sfig-ec-earth3-veg-gbr-dhwmean; @sfig-gfdl-cm4-gbr-dhwmean; @sfig-noresm2-mm-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol; @sfig-access-cm2-gbr-dhwtol; @sfig-ec-earth3-veg-gbr-dhwtol; @sfig-gfdl-cm4-gbr-dhwtol; @sfig-noresm2-mm-gbr-dhwtol) levels of reefs. Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi; @sfig-access-cm2-gbr-logsosi; @sfig-ec-earth3-veg-gbr-logsosi; @sfig-gfdl-cm4-gbr-logsosi; @sfig-noresm2-mm-gbr-logsosi; @sfig-access-esm1-5-gbr-totalconnectivity; @sfig-access-cm2-gbr-totalconnectivity; @sfig-ec-earth3-veg-gbr-totalconnectivity; @sfig-gfdl-cm4-gbr-totalconnectivity; @sfig-noresm2-mm-gbr-totalconnectivity).

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW level for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}

### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`}

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}

### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`}

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}

### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`}

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}

### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`}

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}

### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/log_total_strength_gbr_violin.png){#sfig-noresm2-mm-gbr-totalconnectivity width=`{julia} violin_width`}

>>>>

Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
<!-- 
In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially lower mean thermal tolerance levels compared to reefs in other clusters. However, many bioregions do not show strong differences in thermal tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; @sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol; @sfig-noresm2-mm-bioregion-dhwtol). -->

@@

Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi; @sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi; @sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity; @sfig-access-cm2-bioregion-totalconnectivity; @sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity; @sfig-noresm2-mm-bioregion-totalconnectivity).
<!-- 
## Management area scale clustering

@@

The clusters identified with timeseries clustering at the GBR scale show similar patterns to clusters identified at bioregion and management area scales. Reef depth (@sfig-access-esm1-5-gbr-depth; @sfig-access-cm2-gbr-depth; @sfig-ec-earth3-veg-gbr-depth; @sfig-gfdl-cm4-gbr-depth; @sfig-noresm2-mm-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor; @sfig-access-cm2-gbr-dhwcor; @sfig-ec-earth3-veg-gbr-dhwcor; @sfig-gfdl-cm4-gbr-dhwcor; @sfig-noresm2-mm-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion; @sfig-access-cm2-gbr-initialproportion; @sfig-ec-earth3-veg-gbr-initialproportion; @sfig-gfdl-cm4-gbr-initialproportion; @sfig-noresm2-mm-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels. There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean; @sfig-access-cm2-gbr-dhwmean; @sfig-ec-earth3-veg-gbr-dhwmean; @sfig-gfdl-cm4-gbr-dhwmean; @sfig-noresm2-mm-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol; @sfig-access-cm2-gbr-dhwtol; @sfig-ec-earth3-veg-gbr-dhwtol; @sfig-gfdl-cm4-gbr-dhwtol; @sfig-noresm2-mm-gbr-dhwtol) levels of reefs. Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi; @sfig-access-cm2-gbr-logsosi; @sfig-ec-earth3-veg-gbr-logsosi; @sfig-gfdl-cm4-gbr-logsosi; @sfig-noresm2-mm-gbr-logsosi; @sfig-access-esm1-5-gbr-totalconnectivity; @sfig-access-cm2-gbr-totalconnectivity; @sfig-ec-earth3-veg-gbr-totalconnectivity; @sfig-gfdl-cm4-gbr-totalconnectivity; @sfig-noresm2-mm-gbr-totalconnectivity). -->

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW level for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
<!-- 
![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}
<!-- 
### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`} -->

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}
<!-- 
### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`} -->

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}
<!-- 
### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`} -->

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}
<!-- 
### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`} -->

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}
<!-- 
### Management area scale

@@

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster. Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/log_total_strength_gbr_violin.png){#sfig-noresm2-mm-gbr-totalconnectivity width=`{julia} violin_width`} -->
